Supplememtary examples for:

### 2020-06-15 extensions.Rmd
Add the extensions

library( formatR)
library( knitr)
library( lavaan)
```

```{r, code=readLines("scripthooks.R"), echo=FALSE, results=FALSE}
```

@@

n <- 1000
fe_sem <- readRDS("fe_sem.Rda")
fe_sem.fit <- readRDS("fe_sem.fit.Rda")
```

>>>>

library( formatR)
library( knitr)
library( lavaan)

source("scripthooks.R")
```

@@

n <- readRDS("n.Rda")
waves <- readRDS("waves.Rda")

fe_sem <- readRDS("fe_sem.Rda")
fe_sem.fit <- readRDS("fe_sem.fit.Rda")
```
